Liptschiz

### 2024-02-20 lipschitz/valabstraction.tex
update plots

\begin{tikzpicture}
	\begin{axis}[	axis on top,
				set layers=default,
				xrange=-5:5,
				yrange=-2:2,
				unit vector ratio=1 1 1, scale=1.5,
				view={60}{50},
				]
		\addplot3[fill=blue,opacity=0.1, fill opacity=0.4] 
		coordinates {
	 (0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};

@@

\begin{tikzpicture}
	\begin{axis}[	axis on top,
		set layers=default,
		xrange=-5:5,
		yrange=-2:2,
		unit vector ratio=1 1 1, scale=1.5,
		view={35}{14},
		]
		\addplot3[ fill=blue,opacity=0.1, fill opacity=0.4] 
		coordinates {
			(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};

>>>>

\begin{tikzpicture}
	\begin{axis}[	axis on top, xlabel = \(x_i\),
		ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
				set layers=default,
	xmax = 4, xmin = -4,
ymax = 1, ymin = -1,		
zmax = 1, zmin = -1,
				unit vector ratio=1 1 1, scale=1.5,
				view={60}{50},
				]
		\addplot3[fill=blue,opacity=0.1, fill opacity=0.4] 
		coordinates {
	 (0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};

@@

\begin{tikzpicture}
	\begin{axis}[	axis on top, xlabel = \(x_i\),
		ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
		set layers=default,
				xmax = 4, xmin = -4,
		ymax = 1, ymin = -1,		
				zmax = 1, zmin = -1,
		unit vector ratio=1 1 1, scale=1.5,
		view={35}{14},
		]
		\addplot3[ fill=blue,opacity=0.1, fill opacity=0.4] 
		coordinates {
			(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};
